NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-25 results.tex
draft of aaw section

Next we move on

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_t_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.\\
    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
             and comes from $\deltaEW\approx 10$ in this bin at the 
             edge of the LO phase space.}
    \label{fig:aaw:myy}
  }
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_l1}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y2_l1}
  \caption{
    Azimuthal separation of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.\\
    \comment{MS: Spike in $m_{\gamma_1\gamma_2}$ is in NLO \QCDtEW 
             and comes from $\deltaEW\approx 10$ in this bin at the 
             edge of the LO phase space.}
    \label{fig:aaw:dphi}
  }
\end{figure}

@@

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y1l1l2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y2l1l2_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    the leading photon and the lepton pair (centre), and the subleading 
    photon and the lepton pair (right)
    in diple photon production in association with a lepton pair 
    at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.\\
    \comment{MS: Spike in $m_{\gamma_1\ell_1\ell_2}$ is in NLO \QCDtEW\ 
             and comes from $\deltaEW\approx 10$ in this bin at the 
             edge of the LO phase space.}
    \label{fig:aaz:myy}
  }
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y1_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y1_l1l2}
  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y2_l1l2}
  \caption{
    Azimuthal separation of the leading and subleading photon (left),
    the leading photon and the lepton pair (centre), and the subleading 
    photon and the lepton pair (right)
    in diple photon production in association with a lepton pair 
    at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.\\
    \comment{MS: Spike in $\Delta\phi_{\gamma_1,\ell_1\ell_2}$ is in NLO \QCDtEW\ 
             and comes from $\deltaEW\approx 10$ in this bin at the 
             edge of the LO phase space.}
    \label{fig:aaz:dphi}
  }
\end{figure}

>>>>

Next we move on to diphoton production in association with 
a $W$ boson decaying leptonically.
In this context, we will representatively focus on $W^-$ bosons 
as we do not expect qualitatively different results for $W^+$ 
bosons. 
We define our fiducial phase space by the following. 
First, we require the presence of exactly one charged lepton, 
dressed with all photons in a cone of size $R=0.1$, with 
$\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Among the remaining photons we require at least two identified 
ones, using the procedure described in Sec.\ \ref{sec:results:aaa}, 
only changing the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
We put no requirements on the missing transverse momentum. 
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.
\comment{MS: Nico, please check!}

@@

Figure \ref{fig:aaw:pt} shows the transverse momenta of 
the leading and subleading photon as well as the charged 
lepton. 
As was observed in tiple photon production, the inclusive 
NLO QCD corrections are large. 
Nonetheless, they differ substatially between the three 
oberservables and in their different regions. 
While $\deltaQCD$ rises from values of 0.3 at small 
transverse momenta of the leading photon to 2 at 
$\pT\approx 100\,\text{GeV}$, it remains constant above that 
value.
In the subleading photon's transverse momentum, the 
situation is different. 
Experiencing a cut-induced jump from 0.3 to 2.5 at low \pT, 
it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
at 500\,GeV. 
The behaviour of the QCD corrections to the lepton \pT are 
then again qualitatively similar to that of the leading 
photon, start at $\deltaQCD=0.8$ at low \pT and rising 
steeply to 2.5 at 100\,GeV and then gradually leveling out 
at 3.5. 
Again, the presence of a restrictive jet veto has little 
effect on the small transverse momentum regions, but 
effectively contains the size of the NLO QCD corrections 
to remain below $\deltaQCD=0.5$. 
Instead, they are again driven negative, reaching 
$-20-30\%$ for all three observables.

The electroweak corrections are negative throughout, 
reaching $-20\%$ for the leading photon and the lepton 
and $-20\%$ for the subleading photon at 500\,GeV. 
For this process, starting at transverse momenta of 
around 100\,GeV, the electroweak corrections are much 
larger than the LO uncertainty estimate.
Due to their larger size, as compared with the \aaa\ 
production process, the difference between their 
additive and multiplicative combination with the 
QCD corrections becomes more pronounced when no 
jet veto is applied. 
One reason is that the QCD corrections are dominated 
by real emission contributions, which only receive the 
not-so-small electroweak correction factor in the 
multiplicative combination, but not the additive one. 
While this correction factor is, strictly speaking, 
associated only with the Born configuration, its 
application to real-emission configurations is well 
motivated in the electroweak Sudakov-regime at 
large transverse momenta. 
The concurrence of the additive and multiplicative 
schemes in the presence of the jet veto now precisely 
originates in the taming of the QCD corrections by 
restricting the influence of real-emission topologies.

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_t_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.
    \label{fig:aaw:myy}
  }
\end{figure}

Considering now the invariant mass of both photons 
and the leading photon and the lepton, presented in 
Figure \ref{fig:aaw:myy}, a similar picture 
presents itself. 
Both QCD corrections are moderate at small invariant 
masses and increase as the invariant mass rises. 
While $m_{\gamma_1\gamma_2}$ developes a correction 
factor of $\deltaQCD=2$ at 200\,GeV and then falls 
again to 0.4 at 1\,TeV, $m_{\gamma_1\ell}$ only 
reaches a maximum of $\deltaQCD=1.3$ before falling 
to 0.4 as well. 
In the presence of a jet veto, the shape of the corrections 
remains similar, but their magnitude is contained to 
be smaller than 0.5, turning negative around 500\,GeV 
for both observables. 
The electroweak corrections are again negative 
throughout, reaching $-15-20\%$ at invariant masses 
of 1\,TeV.
Again, above 200\,GeV they are consistently outside 
the LO uncertainty estimate and play an important 
role.

Figure \ref{fig:aaa:myy} also displays the transverse 
mass of the $W$ boson on the right hand side. 
This distribution exhibits the general features known 
from inclusive $W$ production, only the QCD corrections 
are scaled to the values present in this process.
Electroweak corrections are less pronounced than for 
the invariant masses, but are still non-negligible. 
They reach about $-8\%$ at $m_\text{T}=200\,\text{GeV}$ 
and $-14\%$ at 1\,TeV.

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_l1}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y2_l1}
  \caption{
    Azimuthal separation of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.
    \label{fig:aaw:dphi}
  }
\end{figure}

Finally, Figure \ref{fig:aaw:dphi} presents the azimuthal 
separations of the leading and the subleading photon, and 
both the leading and subleading photon and the lepton. 
Contrary to \aaa\ production, no kinematic constraints 
are present at LO, owing to the difference in flavour 
between the considered objects and the fact that the 
lepton is only one of two decay products of the $W$ which 
takes the role of the third photon from point of view of 
the contributing diagrams.

Both the QCD and EW corrections are generally flat, taking 
values of typically $\deltaQCD=1-2$ in absence and 
$\deltaQCD=0.4$ in presence of a jet veto, and 
$\deltaEW=-2\%$.

As none of the observables considered for this process 
exhibits a kinematic boundary at LO that is lifted at 
NLO, both the additive and the multiplicative combination 
of QCD and EW corrections present a viable prediction 
throughout and their difference can be taken as an 
indication of the potential size of higher-order corrections 
of $\order(\alphas\alpha)$.

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Their invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
again loosening the transverse momentum requirements to 
$\pT>20\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
We put no requirements on the missing transverse momentum. 
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.
\comment{MS: Nico, please check!}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y1l1l2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaz/m_y2l1l2_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    the leading photon and the lepton pair (centre), and the subleading 
    photon and the lepton pair (right)
    in diple photon production in association with a lepton pair 
    at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.
    \label{fig:aaz:myy}
  }
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y1_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y1_l1l2}
  \includegraphics[width=0.32\textwidth]{figs_aaz/dphi_y2_l1l2}
  \caption{
    Azimuthal separation of the leading and subleading photon (left),
    the leading photon and the lepton pair (centre), and the subleading 
    photon and the lepton pair (right)
    in diple photon production in association with a lepton pair 
    at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.
    \label{fig:aaz:dphi}
  }
\end{figure}
